\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{lmodern}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{anyfontsize}
\usepackage{enumerate}
\usepackage{pdfpages}
\usepackage{fourier}	% Style
\usepackage{bm}
\usepackage{epstopdf}
\usepackage{lipsum}
\usepackage{authblk}
\usepackage[top=2cm, bottom=3cm, left=2cm, right=2cm, scale=0.75]{geometry}	% Set the margins
\usepackage{fancyhdr}
\usepackage[letterspace=150]{microtype}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{booktabs}
\usepackage{amsmath,etoolbox}
\usepackage{mathtools}
\usepackage{array}
\usepackage{anyfontsize}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{float}
\usepackage[position = top]{subfig}
\usepackage[labelfont=bf,labelsep=period]{caption}
\usepackage{booktabs}
\usepackage{newunicodechar}
\usepackage{booktabs}
\usepackage{nicefrac}	% For diagonal fractions
\usepackage{bbm}
\usepackage{hyperref}	% For hyperlinks

% Packages needed for tables
\usepackage{longtable}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
%\usepackage[framed]{mcode}

% To put footnotes at the bottom of the page
\usepackage[bottom]{footmisc}

% No indent
\setlength\parindent{0pt}

% To enumerate subequations with arabic numbers (e.g. 1.1, 1.2, ecc)
\patchcmd{\subequations}{\def\theequation{\theparentequation\alph{equation}}}{\def\theequation{\theparentequation.\arabic{equation}}}{}{}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}

% Definition of definition environment
\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]

% Definition of theorem environment
\theoremstyle{theorem}
\newtheorem{thm}{Theorem}[section]

% To enumerate the equations and the figures according to the section they are in
\numberwithin{equation}{section}
\numberwithin{figure}{section}

% Path to images folder
\graphicspath{{./img/}}

% To modify the space between figure and caption
%\setlength{\abovecaptionskip}{-2pt}
%\setlength{\belowcaptionskip}{3pt}

\renewcommand{\textfraction}{0.1}
\renewcommand{\topfraction}{0.9}

\renewcommand{\abstractname}{\large Abstract}

\begin{document}

	This document lists different citations and related references which may be useful for the master project.
	
	\section*{Citations}
	
	\begin{itemize}
		\item Multilayer perceptron as an universal function approximator \cite{Cyb89, Fun89} (found in \cite{Tho08})
		\item Optimal brain surgeon: algorithm for network pruning \cite{Has93} (found in \cite{Tho08})
		\item Nguyen-Widrow algorithm: for initialization of weights and biases \cite{Ngu90} (found in \cite{Tho08})
		\item Levenberg-Marquard algorithm: learing algorithm \cite{Tho96} (found in \cite{Tho08})
		\item Error measurement and exemplary problems \cite{Pre94} (found in \cite{Kri07})
	\end{itemize}
	
	\begin{thebibliography}{50}
	
		\bibitem{Cyb89}
		Cybenko G. \emph{Approximation by superposition of a sigmoïdal function}. Mathematics of Control Signals and Systems, 2(4):303-314, 1989.
		
		\bibitem{Fun89}
		Funahashi K. \emph{On the approximate realisation of continuous mapping by neural networks}. Neural Networks, 2:183-192, 1989.
		
		\bibitem{Has93}
		Hassibi B., Stork D. G. \emph{Second order derivatives for network pruning: optimal brain surgeon}. Advances in Neural Information Processing Systems, 5:164-171, 1993.
		
		\bibitem{Kri07}
		Kriesel D. \emph{A brief introduction to neural networks}. Available at \url{http://www.dkriesel.com}, 2007.
		
		\bibitem{Ngu90}
		Nguyen D., Widrow B. \emph{Improving the learning speed of 2-layer neural networks by choosing initial values of the adaptative weights}. Proceedings of the International Joint Conference on Neural Networks IJCNN'90, San Diego, USA, 3:21-26, 1990.
		
		\bibitem{Pre94}
		Prechelt L. \emph{A set of neural network benchmark problems and benchmarking rules}. Technical Report, University of Karlsruhe, Germany, 21:94, 1994.
		
		\bibitem{Tho96}
		Thomas P., Bloch G. \emph{From batch to recursive outlier-robust identification of non-linear dynamic systems with neural networks}. Proceedings of the IEEE International Conference on Neural Networks ICNN'96, Washington D. C., USA, 1:178-183, 1996.
		
		\bibitem{Tho08}
		Thomas P., Choffel D., Thomas A. \emph{Simulation reduction models approach using neural network}. $10^{\text{th}}$ Internal Conference on Computer Modelling and Simulation EUROSIM'08, Cambridge, United Kingdom, 679-684, 2008.
	
	\end{thebibliography}
\end{document}
